---
title: "Demo MDPI to use as template"
titlecitation: "Demo MDPI"
format:
  mdpi-pdf:
    keep-tex: true  
    journal: futuretransp
correspondence: "Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)"
author:
  - name: John Doe
    affiliations:
      - id: 1
        name: University
    orcid: 0000-0000-0000-0000
    email: JD@example.org
    url: https://example.org/
    corresponding: true
  - name: Another Author
    affiliations:
      - id: 2
        name: A different place
abstract: |
  This document is only a demo explaining how to use the template.
keywords:
  - keyword one
  - keyword two
authorcontributions: |
  Use the CRediT taxonomy
studyfunding: |
  Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.
institutionalreview: |
  In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval.
informedconsent: |
  Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.
dataavailability: |
  We encourage all authors of articles published in MDPI journals to share their research data. In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
reference-section-title: References
bibliography: bibliography.bib  
---

# Introduction {#sec-intro}

This is a template illustrating the use of the mdpi quarto extension.

### Shortcode demo {#sec-shortcode}

PDF are rendered using {{< latex >}} but it is best if one can use a Markdown syntax for cross format support.

`{{< latex >}}` used in source is a shortcode syntax where the shortcode is included in the extension folder `_extensions`

### Code chunk {#sec-chunks}

This format hide chunks by default as option has been set in `_extension.yml` file.

```{r}
#| prompt: true
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
```

But you can set `echo` option to `true` locally in the chunk

```{r}
#| echo: true
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
summary(m_pois)
```


### Using references {.unnumbered}

I did not read this book [@CameronTrivedi2013] but it must be interesting. 

Differences between `aft-html` and `aft-pdf`: 

* For the HTML format, we are using Pandoc citeproc to include the bibliography. Here `reference-section-title` controls the title for the chapter that will be used.
* For the PDF format, `natbib` is used by default and the bibliography is included with a title by the LaTeX template. 